D3064R0: OOTA Execution is Provably Vacuous

### 2023-11-30 ootavacuous.tex
Differentiate temporal and atemporal links
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

The speed of light is finite~\cite{OleRoemer1671SpeedOfLight}
and atoms are of non-zero size~\cite{JeanBaptistePerrin1923AtomSize}.
These laws of physics mean that if one thread loads the value
stored by some other thread, that load must have occurred later
in global time than did the store.
Current memory models do not capture these temporal constraints,
which makes it more difficult for them to efficiently rule out
OOTA behavior.

@@

Again, an OOTA cycle consists of loads from other threads' stores where
a given store's address or value depends on the value returned by
the corresponding thread's prior load.
Courtesy of the laws of physics, a given store must execute earlier
in global time than any load from that stored-to object that returns
the value stored.

>>>>

The speed of light is finite~\cite{OleRoemer1671SpeedOfLight}
and atoms are of non-zero size~\cite{JeanBaptistePerrin1923AtomSize}.
These laws of physics mean that if one thread loads the value
stored by some other thread, that load must have occurred later
in global time than did the store.
In other words, the reads-from relation is temporal in nature.

In contrast, the C++11 modification-order relation is atemporal.
This means that the store that executed earlier in global time
might appear later in the stored-to object's modification
order~\cite{McKenney20xxParallelProgramming}.
The atemporal nature of C++11 modification order is due to the hardware
store-buffer optimizations used by modern multicore systems.

Current programming-language abstract machines  do not capture these
temporal constraints, which makes it more difficult for them to
efficiently rule out OOTA behavior.

@@

Again, an OOTA cycle consists of loads from other threads' stores where
a given store's address or value depends on the value returned by
the corresponding thread's prior load.
All of the links from ont thread to the next are reads-from links, which
are temporal in nature, that is, a given store must execute earlier in
global time than any load from that stored-to object that returns the
value stored.
